Taking uncertainty in word embedding bias estimation seriously: a bayesian approach

### 2023-05-17 paper/paperDraft.Rmd
fixed figures

\begin{figure}[H]
```{r visMuslim,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message =FALSE, warning = FALSE}
religion <- read.csv("datasets/cleanedDatasets/religionRedditCleaned.csv")
muslimWords <- c("imam","islam","mosque","muslim","quran")
muslim <- religion %>% filter(protectedWord %in% muslimWords)
muslimClass <- muslim %>% filter(protectedWord == "muslim")
neutralSample <- sample_n(filter(muslimClass,connection == "none"), 5)
humanSample <- sample_n(filter(muslimClass,connection == "human"), 5)
muslimVis <- muslimClass %>% filter(connection != "none" & connection !="human")
muslimVis <- rbind(muslimVis,neutralSample,humanSample)

@@

visualiseProtected(muslimVis,"muslim")+theme_void(base_size = 20)
```

```{r visPriest,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
religion <- read.csv("datasets/cleanedDatasets/religionRedditCleaned.csv")
priestClass <- religion %>% filter(protectedWord == "priest")
neutralSample <- sample_n(filter(priestClass,connection == "none"), 5)
humanSample <- sample_n(filter(priestClass,connection == "human"), 5)
priestVis <- priestClass %>% filter(connection != "none" & connection !="human")
priestVis <- rbind(priestVis,neutralSample,humanSample)

@@

visualiseProtected(priestVis,"priest")+theme_void(base_size = 20)
```

@@

\vspace{1mm}
\footnotesize
```{r generatePlots2,echo=FALSE, eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE, results = FALSE}
source("functions/cleanDataset.R")
source("functions/plotFromPrecis.R")

weat7Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_google.csv")[,-1])
precisWeat7Google <- readRDS("resultsDFs/Weat7GoogleDF.rds")
resultsWeat7Google <- plotFromPrecis(precis = precisWeat7Google,
                                     dataset = weat7Google,
                                     list = "Weat 7",
                                     embedding = "Google",
                                     ylims = c(.75,1.1))

@@

\begin{figure}[H]
```{r fig:debiasedCosinePair2,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", dpi = 300, out.width="85%", warning = FALSE, message = FALSE}

@@

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsWeat7Google$plotJoint
```
\caption{dsds}
\label{fig:weat7google}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsWeat7Glove$plotJoint
```
\caption{dsds}
\label{fig:weat7glove}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsWeat7Reddit$plotJoint
```
\caption{dsds}
\label{fig:weat7reddit}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsWeat1Google$plotJoint
```
\caption{dsds}
\label{fig:weat1google}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsWeat1Glove$plotJoint
```
\caption{dsds}
\label{fig:weat1glove}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsWeat1Reddit$plotJoint
```
\caption{dsds}
\label{fig:weat1reddit}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsReligionGoogle$plotJoint
```
\caption{dsds}
\label{fig:religionGoogle}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsReligionGlove$plotJoint
```
\caption{dsds}
\label{fig:religionGlove}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsReligionReddit$plotJoint
```
\caption{dsds}
\label{fig:religionReddit}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsRaceGoogle$plotJoint
```
\caption{dsds}
\label{fig:raceGoogle}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsRaceGlove$plotJoint
```
\caption{dsds}
\label{fig:raceGlove}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsRaceReddit$plotJoint
```
\caption{dsds}
\label{fig:raceReddit}
\end{figure}

\begin{figure}[H]

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsGenderGoogle$plotJoint
```
\caption{dsds}
\label{fig:genderGoogle}
\end{figure}

\begin{figure}[H]
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsGenderGlove$plotJoint
```
\caption{dsds}
\label{fig:genderGlove}
\end{figure}

\begin{figure}[H]
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsGenderReddit$plotJoint
```
\caption{dsds}
\label{fig:genderReddit}
\end{figure}

\begin{figure}[H]
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsDebiasedReligionReddit$plotJoint
```
\caption{dsds}
\label{fig:debiasedReligion}
\end{figure}

\begin{figure}[H]
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsDebiasedRaceReddit$plotJoint
```
\caption{dsds}
\label{fig:debiasedRace}
\end{figure}

\begin{figure}[H]
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE}
resultsDebiasedGenderReddit$plotJoint
```
\caption{dsds}
\label{fig:debiasedGender}
\end{figure}

>>>>

\begin{figure}[H]
```{r visMuslimd,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",message =FALSE, warning = FALSE}
religion <- read.csv("datasets/cleanedDatasets/religionRedditCleaned.csv")
muslimWords <- c("imam","islam","mosque","muslim","quran")
muslim <- religion %>% filter(protectedWord %in% muslimWords)
muslimClass <- muslim %>% filter(protectedWord == "muslim")
neutralSample <- sample_n(filter(muslimClass,connection == "none"), 5)
humanSample <- sample_n(filter(muslimClass,connection == "human"), 5)
muslimVis <- muslimClass %>% filter(connection != "none" & connection !="human")
muslimVis <- rbind(muslimVis,neutralSample,humanSample)

@@

visualiseProtected(muslimVis,"muslim")+theme_void(base_size = 11)
```

```{r visPriestd,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE}
religion <- read.csv("datasets/cleanedDatasets/religionRedditCleaned.csv")
priestClass <- religion %>% filter(protectedWord == "priest")
neutralSample <- sample_n(filter(priestClass,connection == "none"), 5)
humanSample <- sample_n(filter(priestClass,connection == "human"), 5)
priestVis <- priestClass %>% filter(connection != "none" & connection !="human")
priestVis <- rbind(priestVis,neutralSample,humanSample)

@@

visualiseProtected(priestVis,"priest")+theme_void(base_size = 11)
```

@@

\vspace{1mm}
\footnotesize
```{r generatePlots2h,echo=FALSE, eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE, results = FALSE}
source("functions/cleanDataset.R")
source("functions/plotFromPrecis.R")

weat7Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_google.csv")[,-1])
precisWeat7Google <- readRDS("resultsDFs/Weat7GoogleDF.rds")
resultsWeat7Google <- plotFromPrecis(precis = precisWeat7Google,
                                     dataset = weat7Google,
                                     list = "Weat 7",
                                     embedding = "Google",
                                     ylims = c(.8,1.05))

@@

\begin{figure}[H]
```{r fig:debiasedCosinePair2b,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", dpi = 300, out.width="85%", warning = FALSE, message = FALSE}

@@

<!-- \begin{figure}[H] -->

```{r weatjoint2r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsWeat7Google$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:weat7google} -->
<!-- \end{figure} -->

\pagebreak

<!-- \begin{figure}[H] -->

```{r weat7glovf, echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsWeat7Glove$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:weat7glove} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsWeat7Reddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsWeat7Reddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:weat7reddit} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsWeat1Google,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsWeat1Google$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:weat1google} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsWeat1Glove,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsWeat1Glove$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:weat1glove} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsWeat1Reddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsWeat1Reddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:weat1reddit} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsReligionGoogle,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsReligionGoogle$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:religionGoogle} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsReligionGlove,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsReligionGlove$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:religionGlove} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsReligionReddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsReligionReddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:religionReddit} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsRaceGoogle,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsRaceGoogle$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:raceGoogle} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsRaceGlove,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsRaceGlove$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:raceGlove} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsRaceReddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsRaceReddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:raceReddit} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->

```{r resultsGenderGoogle,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsGenderGoogle$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:genderGoogle} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
```{r resultsGenderGlove,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsGenderGlove$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:genderGlove} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
```{r resultsGenderReddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsGenderReddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:genderReddit} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
```{r resultsDebiasedReligionReddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsDebiasedReligionReddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:debiasedReligion} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
```{r resultsDebiasedRaceReddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsDebiasedRaceReddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:debiasedRace} -->
<!-- \end{figure} -->

<!-- \begin{figure}[H] -->
```{r resultsDebiasedGenderReddit,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300, warning = FALSE, message = FALSE, fig.height= 9, fig.width= 6}
resultsDebiasedGenderReddit$plotJoint
```
<!-- \caption{dsds} -->
<!-- \label{fig:debiasedGender} -->
<!-- \end{figure} -->

### 2023-05-17 paper/paperDraft.tex
fixed figures

\begin{center}\includegraphics[width=1\linewidth]{paperDraft_files/figure-latex/visMuslim-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{paperDraft_files/figure-latex/visPriest-1} \end{center}

@@

\begin{center}\includegraphics[width=0.85\linewidth]{paperDraft_files/figure-latex/fig:debiasedCosinePair2-1} \includegraphics[width=0.85\linewidth]{paperDraft_files/figure-latex/fig:debiasedCosinePair2-2} \end{center}
\caption{Means with 89\% highest posterior density intervals for gender before and after debiasing.}
\label{fig:empiricalDebiasedPair}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-1-1} \end{center}
\caption{dsds}
\label{fig:weat7google}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-2-1} \end{center}
\caption{dsds}
\label{fig:weat7glove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-3-1} \end{center}
\caption{dsds}
\label{fig:weat7reddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-4-1} \end{center}
\caption{dsds}
\label{fig:weat1google}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-5-1} \end{center}
\caption{dsds}
\label{fig:weat1glove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-6-1} \end{center}
\caption{dsds}
\label{fig:weat1reddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-7-1} \end{center}
\caption{dsds}
\label{fig:religionGoogle}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-8-1} \end{center}
\caption{dsds}
\label{fig:religionGlove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-9-1} \end{center}
\caption{dsds}
\label{fig:religionReddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-10-1} \end{center}
\caption{dsds}
\label{fig:raceGoogle}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-11-1} \end{center}
\caption{dsds}
\label{fig:raceGlove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-12-1} \end{center}
\caption{dsds}
\label{fig:raceReddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-13-1} \end{center}
\caption{dsds}
\label{fig:genderGoogle}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-14-1} \end{center}
\caption{dsds}
\label{fig:genderGlove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-15-1} \end{center}
\caption{dsds}
\label{fig:genderReddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-16-1} \end{center}
\caption{dsds}
\label{fig:debiasedReligion}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-17-1} \end{center}
\caption{dsds}
\label{fig:debiasedRace}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/unnamed-chunk-18-1} \end{center}
\caption{dsds}
\label{fig:debiasedGender}
\end{figure}

>>>>

\begin{center}\includegraphics[width=1\linewidth]{paperDraft_files/figure-latex/visMuslimd-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{paperDraft_files/figure-latex/visPriestd-1} \end{center}

@@

\begin{center}\includegraphics[width=0.85\linewidth]{paperDraft_files/figure-latex/fig:debiasedCosinePair2b-1} \includegraphics[width=0.85\linewidth]{paperDraft_files/figure-latex/fig:debiasedCosinePair2b-2} \end{center}
\caption{Means with 89\% highest posterior density intervals for gender before and after debiasing.}
\label{fig:empiricalDebiasedPair}
\end{figure}

@@

\begin{center}\includegraphics{paperDraft_files/figure-latex/weatjoint2r-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/weat7glovf-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsWeat7Reddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsWeat1Google-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsWeat1Glove-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsWeat1Reddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsReligionGoogle-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsReligionGlove-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsReligionReddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsRaceGoogle-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsRaceGlove-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsRaceReddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsGenderGoogle-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsGenderGlove-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsGenderReddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsDebiasedReligionReddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsDebiasedRaceReddit-1} \end{center}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft_files/figure-latex/resultsDebiasedGenderReddit-1} \end{center}
